Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2014-10-01 exp1/present2013.tex
add vskip
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@769 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\setbeameroption{show notes}
\usepackage[utf8]{inputenc}

@@

\note{
  \begin{itemize}
  \item Significance is based on Lenth's method, where he computes a
    pseudo-standard error, since we have only one replicate. This is
    based on computing the median of the absolute effects, and then
    again the median of the smallest effects.
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine''.
  \end{itemize}
}

>>>>

\setbeameroption{show notes}
\usepackage[utf8]{inputenc}

@@

\note{
  \vskip -18pt
  \begin{itemize}
  \item Lenth's method, one replicate: computes a pseudo-standard
    error, median of the absolute effects, and then median of the
    smallest effects.
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit. Do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine''.
  \end{itemize}
}
